
\documentclass[a4paper,10pt]{article}
\newcommand{\mylatex}{\textrm{\LaTeX}}
\usepackage[left=.5in, right=.5in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

% Set section and subsection formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE Jennifer Kathleen Green} \\
    \vspace{0.1cm}
    \href{mailto:jkgreen@sandia.gov}{jkgreen@sandia.gov} \\
    \href{www.linkedin.com/in/jennifer-fisher-green-15a06332}{www.linkedin.com/in/jennifer-fisher-green-15a06332} \\
    \vspace{0.5cm}
\end{center}

\section*{References}
\textbf{James Brandt, 
\textbf{Principal, R\&D S\&E Computer Science, Sandia National Laboratories, Albuquerque, New Mexico - USA} \\
Lead the Monitoring Team Deployment Project by ensuring the availability, reliability, and accessibility of the monitoring service infrastructure and its data analyses for the production resources at Sandia National Laboratory. Provide advanced solutions to Tier 3/4 problems faced in supporting HPC systems, especially surrounding user build and runtime issues, testing, and troubleshooting. Work with the Advanced Architecture team to further their mission of assessing novel architectures for future procurements.


\section*{Conference, Committees \& Programs Participation}
\begin{itemize}
    \item Chair, Reproducibility Committee AD/AE Appendices, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC'2026. Chicago, IL. 2026.
    \item Vice-Chair, Reproducibility Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC'2025. St. Louis, MO. 2025.
    \item Reviewer, Best Papers Selection Committee, 39th IEEE International Parallel \& Distributed Processing Symposium, IPDPS'25. Milan, Italy. 2025. 
    \item Reviewer, IEEE CiSE special issue: Transforming Science through Software: Improving while delivering 100X. Computing in Science \& Engineering. 2025. 
    \item Member, LDMSCON2025 Program Committee, LDMSCON2025: LDMS Users Group Conference 2025. Chicago, IL. 2025
    \item Member, Reproducibility Committee AD/AE Appendices, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC'2022. Dallas, TX. 2022. 
    \item Member, Tutorials Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC'2022. Dallas, TX. 2022. 
    \item Member, Research Posters Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC'2022. Dallas, TX. 2022. 
    \item Member, Student Poster Selection Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC’2019. Denver, CO. 2019. 
    \item Member, Student Volunteer Selection Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC’2019. Denver, CO. 2019. 
    \item Member, Student Volunteer Selection Committee, The International Conference for High Performance Computing, Networking, Storage and Analysis, SC’2018. Dallas, TX. 2018. 
    \item Steering Committee Member, OpenHPC, 2016-2017. 
    \item Member, Student Volunteer Selection Committee, The International ACM/IEEE Conference for High Performance Computing, Networking, Storage and Analysis, SC’2017. Denver, CO. 2017. 
    \item Member, Student Poster Selection Committee. The International ACM/IEEE Conference for High Performance Computing, Networking, Storage and Analysis, SC’2015. Austin, TX. 2015. 
    \item Member, Birds of a Feather Selection Committee. The International ACM/IEEE Conference for High Performance Computing, Networking, Storage and Analysis, SC’2014. New Orleans, LA. 2014. 
    \item Participant, Broader Engagement. The International ACM/IEEE Conference for High Performance Computing, Networking, Storage and Analysis, SC’2011. Seattle, WA. 2011. 
    \item Participant, Broader Engagement. The International ACM/IEEE Conference for High Performance Computing, Networking, Storage and Analysis, SC’2009. Portland, OR. 2009.
\end{itemize}

\end{document}
